\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,margin=0.55in]{geometry}
\usepackage{array}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\renewcommand{\arraystretch}{1.15}
\setlist[itemize]{leftmargin=14pt,itemsep=1pt,topsep=2pt}

\newcommand{\CommonLocation}{MakerWorks Lab, Malad East, Mumbai}
\newcommand{\CommonStipend}{INR 10,000 per month}
\newcommand{\CommonDuration}{2 months, extendable based on performance and project needs}
\newcommand{\CommonCommitment}{Monday to Friday, 9:00 AM to 6:00 PM; Saturdays optional as mutually agreed}
\newcommand{\CommonReporting}{Abhay Waghmare, Lab Director}
\newcounter{rolepage}

\newcommand{\RolePage}[3]{%
  \ifnum\value{rolepage}>0\clearpage\fi
  \stepcounter{rolepage}
  \thispagestyle{plain}
  {\Large\textbf{#1}}\hfill{\small #2}\\
  {\small\textbf{MakerWorks Lab} | Media, Growth, Partnerships}\\[4pt]
  \hrule
  \vspace{6pt}
  #3
}

\newcommand{\DetailsTable}[3]{%
\begin{tabularx}{\linewidth}{>{\bfseries}p{30mm}X}
Openings & #3 \\
Mode & #1 \\
Location & #2 \\
Stipend & \CommonStipend \\
Duration & \CommonDuration \\
Commitment & \CommonCommitment \\
Reporting & \CommonReporting \\
\end{tabularx}
}

\newcommand{\RoleSection}[1]{\vspace{5pt}\par\noindent\textbf{#1}\par\vspace{2pt}}

\begin{document}
\pagenumbering{arabic}
\small

\begin{center}
{\Large\textbf{MakerWorks Lab Media and Growth Internship Openings}}\\
{\small 4 paid openings across Technical Media \& Content and Growth \& Partnerships}
\end{center}

\RolePage{Technical Media \& Content Intern}{Role 1 of 2}{
\DetailsTable{Onsite}{\CommonLocation}{2 openings}

\textbf{Role Summary}\\
The Technical Media and Content Intern will create raw video, photo, and media content for the work happening inside MakerWorks Lab. The role includes shooting with cameras or phones, basic editing, managing social channels, and promoting lab activities, projects, student work, demos, workshops, and research progress.

\RoleSection{Key Responsibilities}
\begin{itemize}
  \item Capture raw videos, photos, process clips, demos, workshops, lab activity, and behind-the-scenes footage.
  \item Shoot with cameras, phones, microphones, lights, tripods, and other basic media equipment.
  \item Edit short-form videos, reels, posts, stories, thumbnails, captions, and simple technical explainers.
  \item Manage and update social channels for lab activities, student projects, workshops, and demos.
  \item Coordinate with engineers, fellows, and interns to capture accurate, safe, and approved project content.
  \item Organize raw footage, edited files, captions, content calendars, publishing notes, and media archives.
\end{itemize}

\RoleSection{Example Work Areas}
\begin{itemize}
  \item Build-in-public reels, student project stories, lab tour clips, workshop highlights, demo explainers, and mentor interviews.
  \item Weekly social media posting support across Instagram, LinkedIn, YouTube Shorts, and other relevant channels.
  \item Content planning around competitions, research milestones, new prototypes, school programs, and public events.
\end{itemize}

\RoleSection{Preferred Skills}
\begin{itemize}
  \item Camera handling, phone videography, basic lighting, framing, and audio awareness.
  \item Basic editing with CapCut, Premiere Pro, DaVinci Resolve, Canva, or similar tools.
  \item Good visual sense, storytelling ability, and interest in technology, robotics, AI, and education.
  \item Reliability, file organization, social media awareness, and comfort working around active lab projects.
\end{itemize}

\RoleSection{Expected Outcomes}
\begin{itemize}
  \item Regular raw and edited media assets for lab activities, demos, workshops, and student projects.
  \item Managed social media updates that promote MakerWorks Lab work clearly and professionally.
  \item Organized media library, captions, post drafts, publishing calendar, and reusable content assets.
\end{itemize}

\textbf{Suitable for:} Media, Design, Mass Communication, Marketing, Engineering, and students who can tell technical stories visually.\\
\textbf{Selection focus:} shooting ability, editing basics, consistency, storytelling, and organized execution.
}

\RolePage{Growth \& Partnerships Intern}{Role 2 of 2}{
\DetailsTable{Remote / Hybrid}{Remote / MakerWorks Lab touchpoints as required}{2 openings}

\textbf{Role Summary}\\
The Growth and Partnerships Intern will reach out to people about MakerWorks Lab programs and offers, get prospects onto calls, provide clear information, help them decide, and support in-person visits, demos, and follow-ups.

\RoleSection{Key Responsibilities}
\begin{itemize}
  \item Research and reach out to schools, parents, colleges, partners, corporates, potential customers, and ecosystem contacts.
  \item Explain MakerWorks Lab programs, workshops, internships, fellowships, demos, labs, and offers clearly.
  \item Get interested prospects onto calls and provide information that helps them make a decision.
  \item Accommodate and coordinate in-person visits, lab tours, demos, meetings, and follow-up conversations.
  \item Maintain CRM sheets, lead status, contact details, call notes, email drafts, follow-ups, and weekly reports.
  \item Protect contact lists, pricing, partner conversations, customer information, and internal business data.
\end{itemize}

\RoleSection{Example Work Areas}
\begin{itemize}
  \item School outreach, parent inquiries, college collaborations, partner demos, workshop leads, and local ecosystem mapping.
  \item Call scripts, WhatsApp follow-ups, email drafts, visit scheduling, demo coordination, and feedback collection.
  \item Weekly reporting on leads, call outcomes, objections, visit interest, conversion blockers, and next actions.
\end{itemize}

\RoleSection{Preferred Skills}
\begin{itemize}
  \item Clear verbal and written communication in English; Hindi or Marathi is a plus for local outreach.
  \item Comfort with calling, email, WhatsApp, LinkedIn, spreadsheets, follow-ups, and professional coordination.
  \item Interest in education, technology, startups, partnerships, sales, and community building.
  \item Persistence, maturity, confidentiality, and ability to update status without being chased.
\end{itemize}

\RoleSection{Expected Outcomes}
\begin{itemize}
  \item More qualified calls, visits, demos, and follow-ups for MakerWorks Lab programs and offers.
  \item Updated lead tracker, outreach logs, call summaries, prospect notes, and weekly progress reports.
  \item Clearer pipeline of schools, parents, partners, customers, and ecosystem opportunities.
\end{itemize}

\textbf{Suitable for:} Management, Marketing, Business, Communication, Engineering, and students interested in startup growth.\\
\textbf{Selection focus:} communication, follow-up discipline, call confidence, trustworthiness, and outcome orientation.
}

\end{document}
